Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-10-08 manuscript.Rmd
bump release number

The interested reader can find the example rendered as a PDF file with real data in the [online supplementary material](https://github.com/aaronpeikert/repro-tutorial/releases/tag/v0.0.2.0-results) and can view the changes we made since preregistering it on this [GitHub page](https://github.com/aaronpeikert/repro-tutorial/compare/v0.0.1.1-prereg..main#diff-e21a8fa2e44b297dfefef329a6ef56d283488d467c4b4ffe2a014111e52a170b).

>>>>

The interested reader can find the example rendered as a [PDF file with real data](https://github.com/aaronpeikert/repro-tutorial/files/7309455/preregistration.pdf) in the [online supplementary material](https://github.com/aaronpeikert/repro-tutorial/releases/tag/v0.0.3.1-results) and can view the changes we made since preregistering it on this [GitHub page](https://github.com/aaronpeikert/repro-tutorial/compare/v0.0.1.1-prereg..main#diff-e21a8fa2e44b297dfefef329a6ef56d283488d467c4b4ffe2a014111e52a170b).
